A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-10-09 paper/ms.tex
add data tables (rvs + phot)

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Evidence for a prograde orbit of Kepler 1627 Ab.} The time of
    each Kepler transit was measured, along with the local slope of
    the light curve.  The two quantities appear anti-correlated, which
    is most easily explained by starspot crossings during the first
    (second) half of transit inducing a positive (negative) TTV,
    provided that the orbit is prograde \citep{mazeh_time_2015}.  The
    units along the abscissa can be understood by considering that the
    stellar flux changes by $\sim$60\,ppt per half rotation period
    ($\sim$1.3\,days).
		\label{fig:corr}
	}
\end{figure}

@@

There are two other new lines of evidence that confirm the planetary
interpretation.  First, the stellar density implied by the transit duration and orbital period
is inconsistent with an eclipsing body around the M-dwarf companion:
we find $\rho_\star = 2.00 \pm 0.24\,{\rm g\,cm}^{-3}$, while the
theoretically expected density for Kepler\,1627B is $\approx 4.6\,{\rm
g\,cm}^{-3}$ (Table~\ref{tab:posterior}; \citealt{choi_mesa_2016}).
The transit duration is therefore too long to be explained by a star
eclipsing the M dwarf secondary at $10$-$\sigma$.  While the planet
might hypothetically still orbit a hidden close and bright companion,
this possibility is ruled out by {\it i)} a lack of secondary lines in
the HIRES spectra and {\it ii)} a lack of secondary rotation signals
in the Kepler photometry.

@@

The second line of confirming evidence comes by analyzing the
individual Kepler transit times. We isolated each of the 144 observed
transits to within $\pm4.5$\,hr of each transit, and fitted each
window with both {\it i)} a local second-order polynomial and transit,
and {\it ii)} a local linear trend.  We let the mid-time of each
transit float, and then calculated the residual between the measured
mid-time and that of a periodic orbit.  This residual, the transit
timing variation (TTV), is plotted in Figure~\ref{fig:corr} against
the local linear slope.  A significant correlation of $-0.0564 \pm
0.0098\ {\rm ppt\,day}^{-1}$ is observed.  Fewer than ten Kepler
Objects of Interest have shown this correlation
\citep{holczer_time_2015}, which is most readily interpreted as a TTV
induced by unresolved starspot crossings \citep{mazeh_time_2015}.
This is only possible if the planet transits the primary star, which
excludes a background eclipsing binary scenario, and therefore
confirms that \pn\ is a planet.  It also suggests that the planet's
orbit is prograde.  The latter point assumes that the dominant
photometric variability is induced by dark spots, and not bright
faculae.  Given the observed transition of Sun-like stellar
variability from spot to faculae-dominated regimes between young and
old ages, we expect this assumption to be reasonably secure
\citep{shapiro_are_2016,montet_long-term_2017,reinhold_stellar_2020}.

@@

\section{Spectroscopic Transit Analysis}
\label{app:rm}

@@

We monitored \sn\ with Keck/HIRES before, during, and after transit on
the night of 2021 Aug 7.  We used the iodine cell for wavelength
calibration\footnote{We considered a line-profile based analysis in
the regions without iodine, but the line profile stability of HIRES
precludes such an approach.}, and extracted the 1-D spectra using the
standard California Planet Survey pipeline \citep{howard_cps_2010}.
The airmass ranged between 1.1 and 2.2 from the start through the end
of observations; the seeing ranged from $1\farcs1$ at the beginning to
$1\farcs5$ at the end.  We also simultaneously observed across {\it
griz} bands using MuSCAT3 at Faulkes Telescope North on Maui, HI.

We considered two approaches to measuring the velocities: in the
first, hereafter ``Method 1'', we cross-correlated against a template
found via spectral classification with \texttt{SpecMatch-Emp}
\citep{yee_SM_2017}.  In ``Method 2'', we used a high S/N template of
V1298~Tau.  Although V1298 Tau is cooler than Kepler~1627A by
$\approx$500\,K, it has a comparable amount of line-broadening ($v\sin
i = 23$\kms), and a comparable level of stellar activity.  The mean
and standard deviation of the internal RV uncertainties averaged over
all epochs were $16.2\pm1.1$\ms\ from Method 1, and $12.6\pm0.6$\ms\
from Method 2.  The corresponding time-averaged reduced $\chi^2$ from
the template match was $1.57\pm0.04$ (Method 1) and $1.30\pm0.02$
(Method 2).  Given these diagnostics, we adopted the velocities from
the second approach.

@@

>>>>

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Evidence for a prograde orbit of Kepler 1627 Ab.} The time of
    each Kepler transit was measured, along with the local slope of
    the light curve.  The two quantities appear anti-correlated, which
    could be explained by starspot crossings during the first
    (second) half of transit inducing a positive (negative) TTV,
    provided that the orbit is prograde \citep{mazeh_time_2015}.  The
    units along the abscissa can be understood by considering that the
    stellar flux changes by $\sim$60\,ppt per half rotation period
    ($\sim$1.3\,days).
		\label{fig:corr}
	}
\end{figure}

@@

There are two other new lines of evidence that confirm the planetary
interpretation.  First, the stellar density implied by the transit duration and orbital period
is inconsistent with an eclipsing body around the M-dwarf companion:
we find $\rho_\star = 2.00 \pm 0.24\,{\rm g\,cm}^{-3}$, while the
theoretically expected density for Kepler\,1627B is $\approx 4.6\,{\rm
g\,cm}^{-3}$ (Table~\ref{tab:posterior}; \citealt{choi_mesa_2016}).
The transit duration is therefore too long to be explained by a star
eclipsing the M dwarf secondary at $10$-$\sigma$.  While the planet
might hypothetically still orbit a hidden close and bright companion,
this possibility is implausible given {\it i)} the lack of secondary lines in
the HIRES spectra and {\it ii)} the lack of secondary rotation signals
in the Kepler photometry.

@@

The second line of confirming evidence comes by analyzing the
individual Kepler transit times. We isolated each of the 144 observed
transits to within $\pm4.5$\,hr of each transit, and fitted each
window with both {\it i)} a local second-order polynomial and transit,
and {\it ii)} a local linear trend.  We let the mid-time of each
transit float, and then calculated the residual between the measured
mid-time and that of a periodic orbit.  This residual, the transit
timing variation (TTV), is plotted in Figure~\ref{fig:corr} against
the local linear slope.  A significant correlation of $-0.0564 \pm
0.0098\ {\rm ppt\,day}^{-1}$ is observed.  Fewer than ten Kepler
Objects of Interest have shown this correlation
\citep{holczer_time_2015}, which can be explained as a TTV
induced by unresolved starspot crossings \citep{mazeh_time_2015}.
This is only possible if the planet transits the primary star, which
excludes a background eclipsing binary scenario, and therefore
confirms that \pn\ is a planet.  It also suggests that the planet's
orbit is prograde.  The latter point assumes that the dominant
photometric variability is induced by dark spots, and not bright
faculae.  Given the observed transition of Sun-like stellar
variability from spot to faculae-dominated regimes between young and
old ages, we expect this assumption to be reasonably secure
\citep{shapiro_are_2016,montet_long-term_2017,reinhold_stellar_2020}.

@@

\section{Spectroscopy and Photometry During the Transit of 2021 Aug 7}
\label{app:rm}

@@

We monitored \sn\ with Keck/HIRES before, during, and after transit on
the night of 2021 Aug 7.  We used the iodine cell for wavelength
calibration\footnote{We considered a line-profile based analysis in
the regions without iodine, but the line profile stability of HIRES
precludes such an approach.}, and extracted the 1-D spectra using the
standard California Planet Survey pipeline \citep{howard_cps_2010}.
The airmass ranged between 1.1 and 2.2 from the start through the end
of observations; the seeing ranged from $1\farcs1$ at the beginning to
$1\farcs5$ at the end.  We also simultaneously observed across {\it
griz} bands using MuSCAT3 at Haleakal\=a Observatory on Maui, HI.
Performing aperture photometry on the latter image stack yielded the
data given in Table~\ref{tab:phot}.

We considered two approaches to measuring the velocities: in the
first, hereafter ``Method 1'', we cross-correlated against a template
found via spectral classification with \texttt{SpecMatch-Emp}
\citep{yee_SM_2017}.  In ``Method 2'', we used a high S/N template of
V1298~Tau.  Although V1298 Tau is cooler than Kepler~1627A by
$\approx$500\,K, it has a comparable amount of line-broadening ($v\sin
i = 23$\kms), and a comparable level of stellar activity.  The mean
and standard deviation of the internal RV uncertainties averaged over
all epochs were $16.2\pm1.1$\ms\ from Method 1, and $12.6\pm0.6$\ms\
from Method 2.  The corresponding time-averaged reduced $\chi^2$ from
the template match was $1.57\pm0.04$ (Method 1) and $1.30\pm0.02$
(Method 2).  Given these diagnostics, we adopted the velocities from
the second approach, which are reported in Table~\ref{tab:rv}.

@@

\input{phot_table.tex}
\input{rv_table.tex}
